Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
Debug

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        select(var.BP, var.CL)

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame %>%
        select(-contains("virus"))

>>>>

```{r maaslin runs, results = 'hide'} 
input_data <- system.file(
    'extdata','example1_features.txt', package="Maaslin2")
input_metadata <-system.file(
    'extdata','example1_metadata.txt', package="Maaslin2")

fit_data <- Maaslin2(
    input_data, input_metadata,'maaslin2_example_output')

if (!file.exists("rds/maaslin.rds")) {

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        select(var.BP, var.CL) %>%
        tibble::rownames_to_column("#")

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame %>%
        select(-contains("virus")) %>%
        select(g_Yersinia, g_Zavarzinella, g_Zhongshania, g_Zobellia, g_Zunongwangia) %>% #DEBUG
        tibble::rownames_to_column("#") %>%
        sample_n(50)
